% References exported from ARANEA Understanding Map
% Drop inside \begin{thebibliography}{...} ... \end{thebibliography}

\bibitem{Brown2004} Brown, J., Gillooly, J., Allen, A., Savage, V., \& West, G. (2004). TOWARD A METABOLIC THEORY OF ECOLOGY.
\bibitem{Chandler2013} Chandler, C., Chari, S., \& Dworkin, I. (2013). Does your gene need a background check? How genetic background impacts the analysis of mutations, genes, and evolution.
\bibitem{Chandler2013b} Chandler, C., Chari, S., Tack, D., \& Dworkin, I. (2013). Causes and Consequences of genetic background effects illuminated by integrative genomic analysis.
\bibitem{Coulson2015} Coulson, T., Plard, F., Schindler, S., Ozgul, A., \& Gaillard, J. (2015). Quantitative Genetics Meets Integral Projection Models: Unification of Widely Used Methods from Ecology and Evolution.
\bibitem{D2014} D., W. (2014). Anthony Cerami award in translational medicine: A journey in science: Early lessons from the hemoglobin field.
\bibitem{Denaro2024} Denaro, C., Stephenson, D., Müller, M., Piccoli, B., \& Azer, K. (2024). Advancing precision medicine therapeutics for Parkinson’s utilizing a shared quantitative systems pharmacology model and framework.
\bibitem{G2016} G., L. (2016). Translational Medicine: Enabling the Proof of Concepts.
\bibitem{J2021} J., D. (2021). Blueprint for pandemic response: Focus on translational medicine, clinical pharmacology and pharmacometrics.
\bibitem{K2020} K., V. (2020). Toward Progress in Quantitative Translational Medicine: A Call to Action.
\bibitem{Lai2018} Lai, P., Liu, H., Cheng, C., Chao, S., \& Lin, H. (2018). Molecular mechanisms and translational medicine application of Oroxylin A in microRNA 155-5p targeting IRF2BP2-NFAT1 axis in sepsis induced lung injury.
\bibitem{Luo2026} Luo, Y., Wu, X., Chen, W., He, Z., \& Yang, Y. (2026). Bioactive plant and fungal metabolites in oral cancer: molecular mechanisms and translational potential.
\bibitem{M2006} M., W. (2006). Translational medicine: Can it really facilitate the transition of research "from bench to bedside"?.
\bibitem{Martins2018} Martins, R. (2018). The conceptual structure of evolutionary biology: A framework from phenotypic plasticity.
\bibitem{Nair2016} Nair, S. (2016). Current insights into the molecular systems pharmacology of lncRNA-miRNA regulatory interactions and implications in cancer translational medicine.
\bibitem{Piperi2018} Piperi, C., \& Papavassiliou, A. (2018). Molecular medicine in the translational research era.
\bibitem{WG2012} W.G., H. (2012). A translational medicine approach to molecular psychiatry.
